\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

\usepackage[finnish]{babel}
% Character encoding
\usepackage[utf8x]{inputenc}
\usepackage[scale=0.75]{geometry}

\firstname{Rodion}
\familyname{Efremov}
\title{Résumé}
\address{Pakkamestarinkatu 1G 113}{00520 Helsinki}
\mobile{+358~40~185~7884}
\email{rodion.efremov@helsinki.fi}
\homepage{http://www.cs.helsinki.fi/u/rodionef}

\begin{document}
\makecvtitle

\section{Education}

\cventry{2008--2014}{Bachelor of Science, Computer Science}{University of Helsinki}{Helsinki}{\textit{grade point average 3.6/5.0}}{}
\cventry{2004--2008}{High School}{Anjalankoski High School}{Kouvola}{}{}

\section{Bachelor thesis}

\cvitem{Title}{\emph{Polunhakualgoritmit ja -järjestelmät} (engl. Shortest path algorithms and systems)}
\cvitem{Description}{I studied and compared several shortest path algorithms, ways to speed up the search such as using bidirectional search, concurrency, heuristic search, graph preprocessing and confining to special graph types. Score: 4/5.}
\cvitem{Download URL}{https://github.com/coderodde/bsc-thesis/blob/master/tutkielma.pdf?raw=true}

\section{Work experience}

\cventry{9.2009--4.2010}{Personal assistant}{City of Vantaa, Health and Social services}{Vantaa}{}{Going to the grocery store, cleaning and making food for my customer with moving disabilities.}

\cventry{5.2009--9.2009}{Process operator}{Oy VR-Rata Ab, Rail-welding unit}{Kouvola}{}{Marking the rails and operating the rail saw.}

\cventry{6.2008--9.2008}{Process operator}{Oy VR-Rata Ab, Rail-welding unit}{Kouvola}{}{Marking the rails and operating the rail saw.}

\cventry{4.2007--6.2007}{Janitor}{Nuorten Kuntoutus Nurku Oy}{Kotka}{}{Keeping a house and its surroundings in order. Gardening and woodwork.}

\section{Languages}

\cvitemwithcomment{English}{fluent}{}
\cvitemwithcomment{Finnish}{fluent}{}
\cvitemwithcomment{Russion}{native language}{}

\section{Technic skills}
\cvitem{Proficient}{Java,  C}
\cvitem{Good}{Javascript, HTML5, CSS}
\cvitem{Intermediate}{SQL}
\cvitem{Basic}{C++}

\section{Technical interest}
\cvitem{}{Unit and integration testing}
\cvitem{}{back-end development}
\cvitem{}{graph algorithms}
\cvitem{}{optimisation algorithms}
\cvitem{}{data structures}
\cvitem{}{machine learning}
\cvitem{}{analytics}

\section{Publications}
\cvitem{\href{https://github.com/coderodde/lce-doc/blob/master/paper.pdf?raw=true}{Computing debt cuts leading to global zero-equity}}{A method for computing such debt cuts in a loan network, that the entire loan network develops into a state, where each and every node has zero equity (the loans may be just ``forgot''). I have produced an \href{https://github.com/coderodde/lce}{\color{blue} implementation} for the method.}

\section{Portfolio}

\cvitem{\href{https://github.com/coderodde/parallelsort}{\color{blue} Parallel radix sort}}{Very efficient, parallel integer sort algorithm for parallel arrays.}

\cvitem{\href{https://github.com/coderodde/ACM-DL-Crawler}{\color{blue} ACM DL Crawler}}{A parallel crawler loading information from ACM web site in order to reconstruct the collaboration graph.}

\cvitem{\href{http://www.cs.helsinki.fi/u/rodionef/pacman/}{\color{blue} Javascript PacMan}}{A Javascript replica of the famous PacMan game.}

\cvitem{\href{http://www.cs.helsinki.fi/u/rodionef/hide/Battleships/dist/Battleships.jar}{\color{blue} Java Battleships}}{A nifty Battleships game clone developed in Java on behalf of a school project. Stores the game state for the user to be able to continue his/her game at the next run of the game.}

\cvitem{\href{https://github.com/biblex2013/biblex}{\color{blue} biblex}}{A stand alone, graphical Java program for managing BibTeX-references persisting information into a SQLite database.}

\cvitem{\href{http://t-rodionef.users.cs.helsinki.fi/multilog/}{\color{blue} multilog}}{A web forum developed on behalf of a web programming course. Stores all the data into a PostgreSQL-database. Supports a user hierarchy of three levels: user, moderator, admin. The entire forum is organized into topics, each containing threads, each containing actual posts. Shows a registered user list of threads containing updates. Allows simple text search. Supporst a simple marking language (italics, bold, monospaced font), and can fix the invalid marking.}

\cvitem{\href{http://t-rodionef.users.cs.helsinki.fi/rateapp/}{\color{blue} rateapp}}{A simple web application allowing a user rate movies and receive recommendations based on the user's ratings. Made on behalf of a school project course.}

\section{Suosittelijat}
\cvitem{Ante Mulari}{Puh. 0505710781, email: ante.mulari@gmail.com, Vala Group Oy, Software development and testing.}

\end{document}